Synpotic Soil Characterization

### 2022-12-28 3-reports/characterization_report.Rmd
update rmd. delete old image files

```{r, icr-vk-regions, fig.height=7, fig.width=16}
tar_read(gg_icr_vankrevelen)$vk_wle
tar_read(gg_icr_vankrevelen)$vk_cb

@@

```{r, icr-unique, fig.height=16, fig.width=16}
tar_read(gg_icr_unique)
```

>>>>

```{r, icr-vk-wle, fig.height=5, fig.width=10}
tar_read(gg_icr_vankrevelen)$vk_wle

@@

```{r, icr-vk-cb, fig.height=10, fig.width=10}
tar_read(gg_icr_vankrevelen)$vk_cb

```{r, icr-unique-wle, fig.height=10, fig.width=4}
tar_read(gg_icr_unique)$vk_unique_wle
```

```{r, icr-unique-cb, fig.height=10, fig.width=7}
tar_read(gg_icr_unique)$vk_unique_cb
```
